Legends for supplementary material

### 2019-03-08 Manuscript/Figures/figure_legends.Rmd
Results review
commented out legends
added legends

**Figure 2: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given a combination of inputs from the ensemble framework. For a particular cell line, contact matrix resolution, and set of features, the data was split into a 7:3 training:testing set ratio.  For the training set, recursive feature elimination was used to reduce the feature space and minimize the influence of uninformative predictors. A particular resampling technique was applied to the reduced training set to create balanced classes. A random forest classification algorithm was then performed and validated using the testing set.

@@

**Figures 4-8. Precision-Recall curves for 10 kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 10 kb resolution data, across each resampling technique. GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).

**Figure 9-13. Recursive Feature Elimination for 10 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 10 kb resolution data were recursively evaluated at different subsets of feature size. For convenience and computational efficiency, feature size decreasing in powers of 2 was considered. The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1. Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).

>>>>

**Figure 2: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given a combination of inputs from the ensemble framework. For a particular cell line, contact matrix resolution, and set of features, the data was split into a 7:3 training:testing set ratio.  For the training set, recursive feature elimination was used to reduce the feature space and minimize the influence of uninformative predictors. [??? Should this be moved?] A particular resampling technique was applied to the reduced training set to create balanced classes. A random forest classification algorithm was then performed and validated using the testing set.

@@

**Figure 4. Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score and MCC for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines. The results presented are for models applied to 10 kb resolution data.

<!--
**Figures 4-8. Precision-Recall curves for 10 kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 10 kb resolution data, across each resampling technique. GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red). 
-->

<!--
**Figure 9-13. Recursive Feature Elimination for 10 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 10 kb resolution data were recursively evaluated at different subsets of feature size. For convenience and computational efficiency, feature size decreasing in powers of 2 was considered. The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1. Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).
-->

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
added legends

>>>>

**Supplementary Figure 3. Heatmaps illustrating the variable reduction.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines. Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red. Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance). The yellow lines separate each of the three predictor types.

**Supplementary Figrue 4. Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores and MCCs for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines. Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives. Bars that appear in the opposite direction (for MCC) indicate a negative correlation between the observed and predicted binary classifications of flanked TAD boundaries.
